Contention management for Cloud RAN over an optical ring

### 2018-06-06 ISCIS/article.tex
commentaires expériences

\begin{prop}
\label{prop:assign}
There is an assignment of the offsets $m_1, \dots, m_k$ on the same position if and only if $k\times ET + RS \leq P$, t
\end{prop}
\begin{proof}
 We fix $m_1 = 0$ and all the offsets will also be at position $0$. 
 Let $u_1,\dots,u_k$ be the nodes attached to the RRHs $1,\dots,k$. We assume that $u_1,\dots,u_k$ are in the order of the ring. The last message emitted by the RRH $1$ arrives at $u_2$ at time $ET - 1 + \omega(u_1,u_2)$. Therefore we can fix $m_2 =  ET  + \omega(u_1,u_2)$. In general we can set $m_i = (i-1) \times ET + \omega(u_1,u_i)$ and all RRHs will use different containers at position $0$ during a period. The assignment is correct, since when the RRH $1$ must emit something in the second period, there is a free container. This later constraint implies that  $k \times ET + \omega(u_1,u_1) \leq P$, which proves the proposition.\qed
\end{proof}

@@

  \paragraph{Experimental evaluation}
In order to evaluate the performances of those methods, we present the cumulative distribution of the latency of the BE traffic latency when the C-RAN traffic is distributed in the slot, or in the period in Fig.~\ref{fig:algocmp}.
Since the previous N-GREEN parameters were too restrictive to put several RRHs on the same position, the parameter $ET$ and has been changed to $400$.

As expected, both of the presented method to optimize the BE traffic latency in the ring are efficient. Indeed, if all the C-RAN packets are sent in the same moment of the period, the chances of having a free container for a BE packet are low. Here, we try to distribute as much as possible the free containers. However, it is important to precise that the parameters induce that there is no free positions during $ET+RS$ unit of time when no repartition is done. This is why the performances of the corresponding curve are so weak.

Since we have observe that the two repartitions are effective, we want to combine them for our {\em reservation algorithm}.  We compare the cumulative distribution of the latency of the BE traffic using the FIFO rule or the reservation algorithm proposed here in Fig.~\ref{fig:optimres}. To keep the same expected load than the load of the experiment if Fig.~\ref{fig:resultopport}, we set $ET = 200$ and $n = 12$. This is not out of context since the exact split (the C-RAN split is the degree of centralization of the computation units in the cloud) of the C-RAN is not fully determined yet~\cite{mobile2011c}. With these parameters, the loss of bandwidth due to reservation is at most $6\%$

>>>>

\begin{prop}
\label{prop:assign}
There is an assignment of the offsets $m_1, \dots, m_k$ on the same position if  $k\times ET + RS \leq P$.
\end{prop}
\begin{proof}
 W.l.o.g we fix $m_1$ so that it is at position $0$ and all the other offsets will then be chosen at position $0$. 
 Let $u_1,\dots,u_k$ be the nodes attached to the RRHs $1,\dots,k$. We assume that $u_1,\dots,u_k$ are in the order of the ring. The last message emitted by the RRH $1$ arrives at $u_2$ at time $ET - 1 + \omega(u_1,u_2)$. Therefore we can fix $m_2 =  ET  + \omega(u_1,u_2)$. In general we can set $m_i = (i-1) \times ET + \omega(u_1,u_i)$ and all RRHs will use different containers at position $0$ during a period. Since $k \times ET + \omega(u_1,u_1) \leq P$ by hypothesis,
 the containers filled by the $k$th RRH are freed before $P$. Hence when the RRH $1$ must emit something in the second period, there is a free container.\qed
\end{proof}

@@

  \paragraph{Experimental evaluation}

  In order to understand the interest of the several refinements of our presented before,

performances of our method, we present the cumulative distribution of the latency of the BE traffic latency in Fig.~\ref{fig:algocmp}. Since the previous N-GREEN parameters were too restrictive to put several RRHs on the same position, the parameter $ET$ and has been changed to $400$.

The performance when we do no packing is really bad, even worst than the methods using an insertion buffer. It is explained by the parameters of the N-GREEN ring: all positions are used and thus, there are no free containers available to BE traffic during $ET+RS$ units of time. When packing the RRHs on a minimal number of positions, the latency decreases dramatically and becomes much better than in the previous methods. The optimizations of spacing inside the slot or inside the period further improve the latency but only marginally. However, in other settings, spacing inside the period is critical as explained before.

  We compare the cumulative distribution of the latency of the BE traffic using the FIFO rule or the reservation algorithm proposed here in Fig.~\ref{fig:optimres}. To keep the load at $90\%$ as in the experiment of Fig.~\ref{fig:resultopport}, we set $ET = 200$ and $n = 12$. This is not out of context since the exact split of the C-RAN (the degree of centralization of the computation units in the cloud) is not fully determined yet~\cite{mobile2011c}. With these parameters, the loss of bandwidth due to reservation is at most $6\%$
